Data Management for LSST Special Programs

### 2023-05-20 sec_sci.tex
Update sec_sci.tex

From a science perspective, however, in some cases where it is \emph{possible} 
to produce such separate data products it is not \emph{necessary}.

While the sections referenced below contain examples, it is ultimately left to 
the discretion of the Rubin Operations Data Managment and System Performance teams 
to decide which Special Programs data products are generated by RDM.

\textbf{Possible but not necessary -- } 
For some science goals, although it would be possible to produce separate 
data products for a Special Program with the LSST Science Pipelines, this 
is not necessary because the visits can be processed with, and included in, 
the WFD data products (Section~\ref{ssec:proc_wfd}).

These cases are usually related to time domain astronomy, difference image
analysis (DIA), prompt processing, and alert production.
Users would simply incorporate the region and program labels in queries to restrict 
their analysis to only a certain Special Program (or only WFD) where the 
science goal requires it.

\textbf{Possible and necessary -- }
For some science goals, users will need distinct data products composed solely from visits associated with certain Special Programs (Section~\ref{ssec:proc_rdm}).

These cases are usually associated with image coaddition and the static-sky catalogs 
of sources detected and measured in the deeply coadded images.

\textbf{Not possible but necessary -- }
For some science goals, users might require unique and separate data products, 
new algorithms or processing routines, and/or significant additional 
computational resources for Special Programs.
In these situations, user processing and user-generated data products will be 
needed (Section~\ref{ssec:proc_user}).

>>>>

From a science perspective, however, in some cases where it is \emph{possible} 
to produce such separate data products it is not \emph{necessary}; these
cases are discussed below.

\textbf{Case A (possible but not necessary due to inclusion in WFD data products) -- } 
For some science goals, although it would be possible to produce separate 
data products for a Special Program with the LSST Science Pipelines, this 
is not necessary because the visits can be processed with, and included in, 
the WFD data products (Section~\ref{ssec:proc_wfd}).
These cases are usually related to time domain astronomy, difference image
analysis (DIA), prompt processing, and alert production.
Users would simply incorporate the region and program labels in queries to restrict 
their analysis to only a certain Special Program (or only WFD) where the 
science goal requires it.

\textbf{Case B (possible and necessary for RDM to create separate data products) -- }
For some science goals, users will need distinct data products composed solely from visits associated with certain Special Programs (Section~\ref{ssec:proc_rdm}).
These cases are usually associated with image coaddition and the static-sky catalogs 
of sources detected and measured in the deeply coadded images.

\textbf{Case C (not possible, so user-generated data products will be needed) -- }
For some science goals, users might require unique and separate data products, 
new algorithms or processing routines, and/or significant additional 
computational resources for Special Programs.
In these situations, user processing and user-generated data products will be 
needed (Section~\ref{ssec:proc_user}).
These cases are usually related to time domain science goals that utilize 
intermediate-timescale ``custom" coadds (e.g., weekly, monthly stacks), 
science goals that require special processing like shift-and-stack techniques, 
or non-standard visits that are outside the boundaries of what the LSST
Science Pipelines can process (Section~\ref{ssec:proc_bounds}).
